---
title: "Multiple Linear Regression Assignment on Customer Data"
author : "Sudharani Rangapale"
date: "July 02 , 2017"
output:
  html_document:
    toc_depth: 3
    toc_float: true
  

---
#Write a code to clear the environment if needed
```{r}
rm(list=ls(all=TRUE))

```

#Write a code to set the working directory.
```{r }
setwd("C:\\Users/Sony/Desktop/csv")
```
#Write a code to read the csv file as "data" as per required
```{r eval=TRUE }
cust_data=read.csv("C:\\Users/Sony/Desktop/csv/CustomerData_Assignment.csv",header=TRUE)

```
#Write a code to know the names of the attributes
```{r}
names(cust_data)

```
#Write a code to find the dimensions of the data
```{r}
dim(cust_data)
```

#Write a code to see the head  and tail of the dataset atleast 10rows
```{r }
head(cust_data,n=10)
tail(cust_data,n=10)
```
#write the code to see datatypes
```{r}
str(cust_data)
```

#Write a code to remove the unuseful variables and store the data 
```{r }
sum(is.na(cust_data))
str(cust_data)
cust_data=cust_data[,-which(names(cust_data) == "City" | names(cust_data)=="CustomerID")]
```
#Write a code to observe the variables and convert them into the required formats
```{r}
  cat_attr=c("FavoriteChannelOfTransaction","FavoriteGame")
  num_attr=c(setdiff(names(cust_data),c("FavoriteChannelOfTransaction","FavoriteGame")))
  cust_data[num_attr]=data.frame(lapply(cust_data[num_attr], 2,FUN=as.numeric))

```
#Check the changes again using str() command
```{r }

str(cust_data)

```
#Write a Code to seperate the target
```{r}
Target_data=cust_data["TotalRevenueGenerated"]

```
#Write a code to get the numerical attributes and categorical attributes and store them numerical attributes as num_df
```{r }

cat_df=cust_data[,cat_attr]
num_df=subset(cust_data,select=num_attr)

```
#Write a code for Normalizing the num_df
```{r}
library(vegan)
num_df=decostand(num_df,method="standardize")
num_df$TotalRevenueGenerated=NULL

```
#Write a code to observe the correlation between the  attributes 
```{r}
cor(num_df)
```
#Write a code to plot the corrplot of correlation between the attributes
```{r}
library(corrplot)

corrplot(cor(num_df), method = "number")

```
#Write a code to combine the numerical,categorical data along with the target 
```{r}
combined_data=cbind(num_df,cat_df,Target_data)
str(combined_data)

```
#Write a code to set the seed and comment why it is used.
```{r}

set.seed(29)

```
# Write a code to get the train rows using sample 

```{r}

train_rows <- sample(x = 1:nrow(combined_data), size = 0.7*nrow(cust_data))

```
#Write a code to get the train and test 
```{r}
train_data <- combined_data[train_rows, ]

test_data <- combined_data[-train_rows, ]

```

#Write a code to just plot the graphs between attributes and targets
```{r}
par(mfrow = c(3,3))
plot(combined_data$ NoOfChildren,combined_data$TotalRevenueGenerated)

plot(combined_data$ MinAgeOfChild,combined_data$TotalRevenueGenerated)

plot(combined_data$ MaxAgeOfChild ,combined_data$TotalRevenueGenerated)

plot(combined_data$ Tenure ,combined_data$TotalRevenueGenerated)
plot(combined_data$ FrquncyOfPurchase ,combined_data$TotalRevenueGenerated)
plot(combined_data$  NoOfUnitsPurchased,combined_data$TotalRevenueGenerated)
plot(combined_data$ FrequencyOFPlay ,combined_data$TotalRevenueGenerated)
plot(combined_data$ NoOfGamesPlayed,combined_data$TotalRevenueGenerated)
plot(combined_data$ NoOfGamesBought,combined_data$TotalRevenueGenerated)


```

#Write a code to form a linear regression model 
```{r}
model_basic=lm(TotalRevenueGenerated~NoOfChildren+MinAgeOfChild+MaxAgeOfChild+Tenure+FrquncyOfPurchase+NoOfUnitsPurchased+FrequencyOFPlay+NoOfGamesPlayed+NoOfGamesBought,data=train_data)

```

#Write a code to plot the model
```{r}
par(mfrow = c(3,3))
plot(model_basic)
```
#Write a code to check the summary of the model 
```{r}
summary(model_basic)
```
#Write a code to predict the value of the target on the linear model 
```{r}
without_target=num_attr[-length(num_attr)]
pred_values_ln=predict(model_basic,test_data[without_target])
```

#Write a code to use stepAIC
```{r}
library(MASS)
model_aic <- stepAIC(model_basic, direction = "both")

summary(model_aic)

par(mfrow = c(3,3))

plot(model_aic)

summary(num_df)

```

#Write a code to predict it on stepAIC
```{r}

pred_values_aic=predict(model_aic,test_data[without_target])
```
#Write a code to check the multicollinearity in the lm model 
```{r}
library(car)

vif(model_basic)
```

#Write a code to check the multicollinearity problem
```{r}

vif(model_aic)


```

### Error Metrics for Regression

```{r}
#Mean Absolute Error (MAE)
mae <- function(actual, predicted){
 
 error <- actual - predicted
 
 mean(abs(error))
 
}

#Mean Squared Error (MSE)

mse <- function(actual, predicted){
 
 error <- actual - predicted
 
 mean(error^2)
 
}

#Root Mean Squared Error (RMSE)
rmse <- function(actual, predicted){
 
 error <- actual - predicted
 
 sqrt(mean(error^2))
 
}

#Mean Absolute Percentage Error (MAPE)
mape <- function(actual, predicted){
 
 error <- actual - predicted
 
 mean(abs(error/actual))*100
}
 ```
 
 #Write a code to evaluate the error in the prediction of AIC

```{r}
mae(test_data$TotalRevenueGenerated, pred_values_aic)
mse(test_data$TotalRevenueGenerated, pred_values_aic)
rmse(test_data$TotalRevenueGenerated, pred_values_aic)
mape(test_data$TotalRevenueGenerated, pred_values_aic)

# OR

library(DMwR)

regr.eval(test_data$TotalRevenueGenerated, pred_values_aic)



```
#Write a code to evaluate the error on the prediction of Linear Regression
```{r}
mae(test_data$TotalRevenueGenerated, pred_values_ln)
mse(test_data$TotalRevenueGenerated, pred_values_ln)
rmse(test_data$TotalRevenueGenerated, pred_values_ln)
mape(test_data$TotalRevenueGenerated, pred_values_ln)

# OR

regr.eval(test_data$TotalRevenueGenerated, pred_values_ln)



```



#stepAIC by removing tenure
```{r}
new_model <- lm(formula = TotalRevenueGenerated~NoOfGamesBought+NoOfChildren+MinAgeOfChild+MaxAgeOfChild+FrquncyOfPurchase+FrquncyOfPurchase+NoOfUnitsPurchased+FrequencyOFPlay+NoOfGamesPlayed +NoOfGamesBought,data = train_data)
summary(new_model)

without_target1=num_attr[-length(num_attr)]
pred_values_ln1=predict(new_model,test_data[without_target])

regr.eval(test_data$TotalRevenueGenerated, pred_values_ln1)
vif(new_model)

```



